JWST Noise Floor I: Systematic Error Sources with JWST NIRCam Time Series

### 2020-04-29 ms.tex
tiny modification to abstract
reorganized and got rid of everything going in paper 2

\usepackage{graphicx}
\usepackage{float}
\usepackage[caption=false]{subfig}
\usepackage{enumitem}

@@

\title{Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors}

@@

\author{Rafia Bushra}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

\author{Stephanie Striegel}
\affiliation{Department of Physics \& Astronomy \\
San Jose State University \\
One Washington Square \\
San Jose, CA 95192, USA}
\affiliation{NASA Ames Research Center \\
Space Science and Astrobiology Division \\
Moffett Field, CA 94035, USA}

\author{Xander Levinson}
\affiliation{Department of Astronomy \& Astrophysics \\
University of California, Santa Cruz \\
1156 Highland Street \\
Santa Cruz, CA 95062, USA}
\affiliation{NASA Ames Research Center \\
Space Science and Astrobiology Division \\
Moffett Field, CA 94035, USA}

\author{Karl Misselt}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

\author{Jarron Leisenring}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

\author{Kenneth Don}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

\author{Douglas Kelly}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

\author{Thomas Beatty}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

\author{Thomas P Greene}
\affiliation{NASA Ames Research Center \\
Space Science and Astrobiology Division \\
Moffett Field, CA 94035, USA}

@@

JWST transmission and emission spectra of transiting exoplanets will provide invaluable glimpses at exoplanet atmospheres.
These spectra will reveal the composition and temperature structure at a level never achieved before.
This promising science from JWST, however, will require exquisite precision and understanding of systematic errors that can impact the time series of planets crossing in front of and behind their host stars.
This is especially true if JWST is used to search for biosignatures in temperature atmospheres on Earth-sized planets that may contain liquid water.
Here, we provide the lessons learned from ground-based characterization of the NIRCam H2RG detectors, which will be used for exoplanet spectra.
%and are the same type of detectors used in JWST's NIRISS and NIRSpec instruments.
We summarize the lessons learned from tests at NASA Goddard, NASA Johnson and the University of Arizona detector lab.
Correlated electronic noise (1/f noise) in the detectors can limit the sensitivity of grism time series for a given frame (300 ppm to 1000 ppm depending on the extraction method), but will average down like $\sqrt{N}$ for $N$ frames.
Care should be taken to include as many frames as possible per visit to reduce this 1/f noise source: thus, we recommend the smallest detector subarray sizes one can tolerate, 4 output channels and readout modes that minimize skipped frames (RAPID or BRIGHT2).
Pointing jitter and high gain antenna moves on top of the detectors' subpixel crosshatch patterns will produce relatively small variations $\lesssim 10$ ppm, before they are corrected.
In contrast to the HST WFC3 detectors, persistence due to charge trapping will have a negligible effect on time series.
Future performance tests during commissioning and the early release science will still be needed to assess the noise floor on stars, which are more stable than the available LED lamps used in lab-based tests.
\end{abstract}

@@

Section \ref{sec:knownEffects} lists the known systematic effects that can impeded high precision time series and increase the noise above the photon and read noise.
Section \ref{sec:experiments} describes the experiments on the ground that are used to prepare for JWST observations in flight.

\section{Known Detector Effects}\label{sec:knownEffects}
An ideal HgCdTe detector simply counts the photons incident on its surface (as described in section \ref{sec:detectorPrimer}).
However, there are many non-ideal effects that can affect the stability of a light curve of a transiting exoplanet.
Here, we review many of the known noise sources that could impact the stability of a time series beyond photon counting statistics. These known detector effects that can impact stability are listed briefly and then in more detail as related to the JWST NIRCam detectors below that.

@@

\subsection{Pre-amp Reset Offsets from the Lockheed CV Test}\label{sec:preAmp}

@@

\subsection{1/f Noise}
The readout circuitry for NIRCam and other JWST NIR instruments introduces correlated noise from pixel-to-pixel.
This is visible when examining the time series of pixels as they are read out within a frame in the order they are addressed.\footnote{See a diagram of the readout directions at \url{https://jwst-docs.stsci.edu/near-infrared-camera/nircam-instrumentation/nircam-detector-overview/nircam-detector-readout}}
The power spectrum of this pixel-by-pixel time series reveals high power at low frequencies that drops approximately like a 1/f power law in the power spectrum of the time series.
Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from amplifier over 108 dark frames.
To create the periodogram, the reference pixels are used to remove amplifier offsets between frames.
Next, the average of all frames is subtracted to remove the bias and all pixels that deviate by more than 80 DN from the average are masked to eliminate bad pixels.
The periodogram shows many spikes at high frequency including one at the line reset time of 524 clock cycles, which is the time to read out all the pixels in a row for the amplifier and line overheads before moving to the next row.

@@

\subsection{Fringing}

\clearpage
\subsection{Subpixel Crosshatching}

\subsubsection{Crosshatch Pattern Modeling}
We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency than in spatial coordinates as seen in Figure \ref{fig:crossHatchA5}.
We divide the 2D Fourier power spectral density by the number of pixels in an input image.
This was experimentally determined to give a power spectral density that does not change with the dimensions of the input image.
\textcolor{red}{Can we justify this more? I thought it would be pixels$^2$}

\clearpage
\subsubsection{Position of SubGrism Array}

\subsubsection{Subpixel Crosshatching Calculation}\label{sec:CrosshatchSim}

\subsubsection{Time Series Simulation}
The JWST fine steering mirror (FSM) is designed to correct any telescope pointing errors that are not full corrected by the reaction wheels.
The JWST attitude control system team provided a simulation of the expected pointing performance shown in Figure \ref{fig:tserPointingFull}.

\subsection{Random Telegraph Noise and RC pixels}
Several pixels exhibit RC (exponential) behavior and other exhibit unpredictable jumps in their DC levels.
The jumps are called Random Telegraph Noise (RTN) and some examples are shown in Figure \ref{fig:RTNandRC}.
These are rare events (400-1000 pixels out of 4$\times 10^6$) so they are unlikely to end up in a grism or in-focus aperture.

\clearpage
\section{Ground-based Experiments}\label{sec:experiments}

Table \ref{tab:testSummary} contains a summary of the ground-based tests that were performed on NIRCam detectors.
The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum Test 3 (CV3) as well as OTIS (Optical Telescope Element and Integrated Science).
We also used dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
The GL dewar experiments used flight-like detectors, but a different controller (Leach).
The Asic dewar located at Steward Observatory in Tucson, Arizona used the same kind of detectors as NIRCam, the same kind of asic controllers and the same flight software, but no flight-like optics.
These two different kinds of detector electronics can be compared against each other to help isolate optical-related systematics, detector-related systematics and electronics-related systematics.

The instrument modes tested included mostly imaging with narrowband LEDs, but there was also a test with spectroscopy on a broadband source.
The one test with a broadband source was an OTIS stability test at NASA Johnson was a grism spectroscopy mode, which illuminated the long wavelength detector with a slitless spectrum covering 2.4 to 4.0~$\mu$m for the F322W2 filter, as seen in Figure \ref{fig:ampOffsetsOtisGrismSlope}.
The WLP8 imaging tests are where a point source is de-focused by 8 waves with a weak lens (WLP8), as shown in Figure \ref{fig:WLP8PSF}.
This mode was designed for wavefront sensing, but is also useful for high-precision time series because it spreads the light over many pixels.
The weak lens produces a point spread function (PSF) that is hexagonal like JWST's mirrors and has a flat-to-flat width of $\sim$108 pixels and a vertex-to-vertex width of $\sim$136 pixels.
The hexagonal PSF also has a central vertical peak which can be used for aperture centering.
The tests with the GL and ASIC dewars did not have NIRCam optics and instead were flood illuminated with a light source that had large spatial variations due to a non-uniform source.

\begin{deluxetable*}{ccCrlccc}[b!]
\tablecaption{Summary of Ground-Based Tests}\label{tab:testSummary}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Name} &
\colhead{Location} &
\colhead{Test Year} &
\colhead{Best Stability} & 
\colhead{Light Source} & 
\colhead{Instrument Mode} &
\colhead{Flight Hardware?}&
\colhead{Controller} \\
\colhead{} &
\colhead{} &
\colhead{(YYYY)} &
\colhead{(ppm)} &
\colhead{} &
\colhead{} &
\colhead{} &
\colhead{}
}
\startdata
%Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & \nodata \\ 
%Reset per int test & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & Y \\ 
CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging & Y & Asic \\
OTIS       & NASA Johnson  & 2017       &      	& Continuum     & Darks & Y & Asic\\
OTIS       & NASA Johnson  & 2017       &   2200    	& Continuum     & Grism spectroscopy & Y & Asic\\
OTIS       & NASA Johnson  & 2017       &   21,000    	& Continuum     & WLP8 Imaging & Y & Asic\\
GL dewar   & U of Arizona  & 2015-2016  &       	& LED	        & flood-illuminated imaging & N & Leach\\
Asic dewar & U of Arizona  & 2017-2019  &       	& LED           & flood-illuminated imaging & N & Asic\\
\enddata
\tablecomments{Cryogenic vacuum (CV), Optical Telescope element and Integrated Science (OTIS).}
\end{deluxetable*}

\clearpage
\subsection{Long Darks}\label{sec:longDarks}

@@

\subsubsection{Mean Row by Amplifier}\label{sec:indAmpAvg}
A slight modification to the above strategy is to average each amplifier individually.
This takes care of any differences between amplifiers.
This individual amplifier dramatically decreases the errors.
The standard deviations of the background-subtracted photometry range from 2,540 to 3,300 DN or 65 to 85 ppm.
Therefore, this simple approach can dramatically decrease the 1/f noise to below the photon limit.
This is possible for Weak Lens photometry but not grism spectroscopy when dispersed parallel to detector rows (the fast-read direction).

\subsubsection{Smoothed Kernel Subtraction}\label{sec:smoothKernelSub}

@@

\subsubsection{Reference Channel Subtraction}
We note that the 4 channels can sometimes exhibit the same 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by un-illuminated channels.
We attempt to subtract an amplifier 0's time series from all amplifiers.
Of course, this means that this amplifier is perfectly subtracted and no noise or signal remains in this 1/4 of the image.
The subtraction step should increase the read noise on an individual pixel by $\sim \sqrt{2}$ because the errors from the subtracted pixel should add in quadrature to the original pixels.
This increase in read noise on a per-pixel level might be acceptable if it decreases the correlated errors along the rows.
On the other hand, if the each amplifier exhibits its own individual correlated noise behavior, the reference amplifier will fail to subtract out all correlated noise and may introduce more noise.

@@

\subsubsection{PCA Correction}
Another approach to treating the 1/f noise is dimensionality reduction with Principal Component Analysis.
Here, we assume that the counts for each pixel along a column is a random variable that can be correlated with pixels in other columns.
Each row represents a different noise iteration.
First, we calculate the mean value of each pixel in the 108 group stack and subtract all groups by this mean image.
This removes all bias levels and focuses on the time variability of the pixels.
Here, we assume the dark current is negligible.
Next, we mask all bad pixels by setting all pixels with $| f | > 200$ DN to 0 DN to remove bad pixels that can drive the principal components.
The first 10 principal components are plotted in Figure \ref{fig:pcaEigenvectors} for two example groups (54 and 55).

@@

\subsubsection{Grism Aperture}
The NIRCam grism time series are particularly susceptible to 1/f noise because the dispersion direction is parallel to the detector's fast-read direction.
This is visible in Figure \ref{fig:longDarkGrism} where the grism apertures (in red) are parallel to the 1/f noise correlations.
The background subtraction along the spatial direction (vertically) will efficiently remove pre-amplifier offsets from frame to frame and amplifier to amplifier.
However, there are no side reference pixels or horizontally-offset background regions available on the middle two amplifiers.
Therefore, the 1/f noise will adversely impact broadband behaviors of the lightcurves, especially on the middle two amplifiers.

@@

\subsubsection{Optimally Co-Variance Weighted Flux}\label{sec:optimalCovWeights}

@@

\subsubsection{Empirical Covariance Matrix}\label{sec:empCovarianceMatrix}
The ideal weighting of the spectrum from Equation \ref{eq:covarianceweights} depends on the covariance matrix $C_{ij}$.
We use CDS (correlated double sampling) read pairs of OTIS long dark data (108 frames) with reference pixel corrections to estimate $C_{ij}$.
We consider a wavelength bin that is 100 pixels in the dispersion direction (0.1$\mu$m) and 14 spatial spatial pixels.
We also subtract the CDS frames by the median of each row-by-row and the median of each column column-by-column to reduce the amplifier offsets and 1/f noise as done in Figure \ref{fig:longDarkPhot}.

@@

%% See the notebooks wlp8_psf_image.ipynb and noise_sources_wlp8.ipynb for calculations
\subsubsection{The impact of correlated read noise on time series}
We consider here some example science impacts of correlated read noise in these photometric apertures.
We will evaluate the performance of a WEAK LENS +8 mode photometric time series, as will be common with NIRCam grism time series observations.
For a pessimistic scenario, we assume a 15,000 DN read noise contributes to every pair of reads for the 70 pixel radius aperture (and 75 to 100 pixel background subtraction annulus).
If the read noise is tolerable under this scenario, then it should have a minimal impact on photometric time series.
If it is a problem, we will discuss methods of mitigation such as the row-by-row subtraction above.

@@

\subsubsection{Impact to Grism Time series}
We consider a 0.17$\mu$m-wide wavelength bin and 20 pixel aperture diameter as a test case for how badly it will impact spectroscopic features that are 0.17$\mu$m wide.
In this case, we assume row-by-row subtraction is performed and that the CDS noise from the OTIS ground-based test is representative of flight.
Then, the equivalent grism aperture noise to equation \ref{eq:bestRNCorrection} is
\begin{equation}
RN_{grism,0.17\mu\mathrm{m}} = \frac{5,130 DN}{ \sqrt{N_{frames}}}.
\end{equation}
For the grism aperture

\subsection{Goddard Cryogenic Vacuum (CV) Stability Tests}

During the Cyrogenic Vacuum Test 3, the Integrated Science Instrument Module (ISIM) was placed in a vacuum chamber with the Optical telescope element simulator (OSIM).
The ISIM has all the instruments with their internal optics and detectors but no telescope mirrors.
The OSIM simulates the PSF expected when a star or other point source illuminates the JWST instruments.
The point spread functions from CV3 most closely resembled the JWST flight point spread function and WLP8 defocused image of all ground based tests discussed in this work.
Although the light curves from the CV3 stability tests were not able to achieve photon-limited performance to study the precision of transit and eclipse spectroscopy, there were some lessons learned from this data.

\subsubsection{Comparison of Subarray and Full Frame Stability Tests}

CV3 included a series of exposures about 16 hours with an LED lamp in imaging mode to test the fundamental photometric performance.
The LED was a narrowband source at 1.55 $\mu$m, which was used in imaging mode since this would result in a narrow-lined spectrum.
While the spectroscopic modes are expected to be the most scientifically interesting modes for studying exoplanet atmospheres, the broadband lamps needed to produce a spectrum tend to be less stable than LEDs.
Therefore, the test was designed with an LED with the hope of measuring the precision possible with the NIRCam optics and detector.

As with the spatial scanning mode on HST \citep[e.g.][]{mccullough2012spatialScan,deming13}, spreading the light of a source over many pixels can improve the precision of spectroscopy.
This is also accomplished by ground-based observatories by either de-focusing the telescope \citep{southworth2009defocusing} or by employing a beam-shaping diffuser \citep{stefansson2017diffusers}.
By spreading the light source over many pixels, the light curve becomes less sensitive to flat fielding or intra-pixel sensitivity errors with telescope pointing jitter or seeing variations during an observation.
Similarly, NIRCam time series observations can employ a weak lens to defocus a star's light.
Figure \ref{fig:WLP8PSF} show the PSF of the +8 wave defocused images during the CV3 stability tests.

We applied the ramps-to-slopes pipeline \texttt{nchdas} to do reference pixel correction, apply a bad pixel mask and calculate slopes or differences of the reads.
The reference pixel correction uses the top/bottom pixels to remove pre-amp resets and side reference pixels to reduce the 1/f noise.
The hexagonal PSF is summed with circular aperture with a radius of 70 pixels and a background annulus spanning from 75 to 100 pixels using the \texttt{photutils} package \citep{bradley2016photutilsv0p3}.
The central peak may used to find a centroid of the star and center the circular aperture.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{wlp8_psf.pdf}
\caption{Weak Lens +8 PSF during CV3 testing.
The central peak is used for centroiding, while the entire PSF is used for aperture photometry.
A 70 pixel radius aperture (shown here is a black circle) is used for the source aperture.}\label{fig:WLP8PSF}
\end{figure}

The LED lamp was coupled to optical fibers to illuminate two separate detectors simultaneously with the intention of having two independent measurements to compare.
Unfortunately, vibrations and jitter in the optical setup affect the relative flux in the two fibers.
The coupling mechanism into the fibers is sensitive to the lamp position, so the flux from the two detectors is highly anti-correlated, as shown in Figure \ref{fig:CV3longTserAB}.
To redice this fiber coupling effect, we average the flux from the two detectors for the rest of this discussion.
This reduces the standard deviation of the time series to 500-1500 ppm.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.39\columnwidth]{cv3_A_vs_B_all.pdf}
\caption{The light from an LED lamp is split into two optical fibers, which are highly anti-correlated likely because vibrations move the lamp relative to the fibers to couple one fiber better than the other.
Here, the time series fit to a second order polynomial in time to remove long term trends and then the aperture flux for two detectors' fluxes are plotted against each other.
For the discussion of CV3 tests forward, we average the two detectors (A1 and B4) to reduce this effect.}\label{fig:CV3longTserAB}
\end{figure}

A series of detector stability tests was performed using this +8 wave weak lens and 1.55 $\mu$m LED in a few different modes.
A time series of all possible modes is shown in Figure \ref{fig:CV3longTser}.
The full frame modes (FULL1 through FULL6) used 2 samples of the ramp for integration times of 21.5 seconds whereas the subarrays were tuned to have a similar integration time (21.3 sec for 20 Groups of a 320$\times$320 subarray and 25.1 seconds for 6 groups of a 640$\times$640 subarray).
This ensured that during these 4 different types of subarray/full frame window sizes, the well depths achieved were similar.
However, the groups are fit to a line for each pixel, so the useful portion of the ramp is the time between the last and first read or 20.2 seconds for the 320$\times$320 subarray versus 10.7 seconds for the FULL1 through FULL6 tests.

It is apparent from Figure \ref{fig:CV3longTser} that the WLP8SUB test with a 320$\times$320 subarray and 20 groups of the ramp has smaller scatter on short timescales than the FULL1 through FULL6 tests.
After removing a linear fit to the time series (to account for long term trends in the lamp), the standard deviation of the WLP8SUB data is 500 ppm whereas the FULL tests range from 1020 to 1540 ppm.
For the FULL 2048$\times$2048 pixel integrations with 2 groups up the ramp, the count rate of photons is calculated in each pixel by subtracting the two groups (ie two reads for this RAPID mode) from each other and dividing by the group time (time between these two reads for this RAPID mode).
For the WLP8SUB mode, a linear least squares fit is performed to the groups as a function of time and the slope of this line is the count rate on a pixel.
The large number of groups used to fit this line ensures that the read noise is reduced as compared to the FULL 2 group tests by $2/\sqrt{N_G}$, where $N_G$ is the number of groups.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.79\columnwidth]{plot_mmm.pdf}
\caption{Time Series plot through the CV3 photometric stability campaign.
All test shown above were using the Weak Lens +8 mode, with a PSF as shown in Figure \ref{fig:WLP8PSF}.
13 tests (FULL1 through FULL6) are all in full frame mode, while SUB used a 320$\times$320 subarray and SUB640 used a 640$\times$640 subarray.
The WLP8SUB showed smaller standard deviation that the full frame tests, when the linear trend is removed.}\label{fig:CV3longTser}
\end{figure}

We consider two explanations for why the WLP8SUB mode shows less scatter than the FULL modes, 
\begin{enumerate}[noitemsep]
	\item The reduction of read noise improves the stability of the signal and\label{item:readNReasonCV3subFull}
	\item That the lamp is variable on short time scales of a frame (10.74 seconds) and sampling.\label{item:lampReasonCV3subFull}
\end{enumerate}
As listed in Table \ref{tab:noiseSummary1overf}, the theoretical uncorrelated read noise for double-correlated samples (CDS) is about 33 ppm.
However, the dark frame tests in Section \ref{sec:longDarks} show that 1/f noise significantly increases this value.
When reference pixel corrections are applied to the data and a 70 pixel source radius is used, the measured CDS read noise from the dark test is 280 ppm for the long wavelength detector.
Due to the source lamp setup discussed in Figure \ref{fig:CV3longTserAB}, we average the flux from detector A1 and B4, which lowers the read noise by $\sqrt{2}$  to 200 ppm.
As a check, we perform aperture photometry on an un-illuminated regions of the time series stability tests and average the results of the two detectors.
We find a standard deviation of 1100 to 1490 e$^-$/s or 150 ppm to 200 ppm of the 7.5$\times 10^6 e^-$/s flux, likely due to slight differences in the 1/f noise within the exposures.
So, the measured standard deviation of ~1000 ppm during the full-frame tests is due largely to lamp variations and not read noise alone.

The WLP8SUB integrations had 20 groups, so the measured read noise should be 280 ppm $\times \sqrt{2/20}$= 89 ppm.
There is no un-illuminated region of the 320$\times$320 subarray that is as big as the source aperture so there is not empirical check on this 89 ppm estimate.
The difference of 83 ppm between the measured full frame read noise and the calculated subarray is not enough to explain the full difference in precision between the two tests.
Thus, we rule out \ref{item:readNReasonCV3subFull} as the main noise source.
Instead, we conclude that the lamp has significant short-timescale variability that the faster samples used on the SUB320 test can average over.
%The take-away from the comparison between subarrays is that one can reduce the read noise and short timescale variability with more samples up the ramp and a smaller subarray.

\subsubsection{Row-by-row Background Subtraction}

Even though we rule out read noise as the dominant noise source, we investigate ways to reduce the fractional contribution of read noise.
If we use a row-by-row subtraction, as discussed in Section \ref{sec:indAmpAvg}, the read noise can be reduced.
We use a procedure that reduces the 1/f electronic noise.
First, we find the robust mean flux for each row of the background annulus with radii of 95 and 195 pixels.
We then, subtract this value from the entire row of the image and perform aperture photometry on the residual image surrounding the source with a circular aperture of 70 pixels.
This procedure reduces the measured read noise on a dark (un-illuminated) region to 60 to 100 ppm.

\subsubsection{Best Pipeline Practices from CV3 Tests}\label{sec:CV3Lessons}

\begin{figure*}
\gridline{\fig{ES-WLP8SUB_pipeline_parameters.pdf}{0.39\textwidth}{SUB320 Time Series}
\fig{{ES-FULL4_pipeline_parameters.pdf}}{0.39\textwidth}{FULL4 Time Series}}
\caption{Flat fielding, linearity corrections and intrapixel capacitance corrections have a relatively small impact on the time series precisions measured during the CV3 test.
Each table lists the measured noise (in ppm) when we turn on/off IPC correction (vertical direction), flat fielding (horizontal direction) and the linearity correction (diagonal direction).
The IPC and flat fielding corrections are negligible.
Above 50\% well depth, the HgCdTe detectors become less sensitive to photons, so applying the linearity correction naturally increases the apparent noise.
}\label{fig:CV3pipeParamsWLP8}
\end{figure*}

We investigated best practices for the pipeline and analysis by running the raw data through the pipeline and sequentially adding and subtracting steps that go into producing light curves.
We experimented with the methodology for turning raw detector reads up the ramp into count rates on the detector, the intrapixel capacitance (IPC) correction, flat fielding, reference pixel correction and detector non-linearity.
After the calibrated images are created, we experimented with different types of aperture photometry including different geometries, background calculations and aperture sizes.

We find that the intrapixel capacitance (IPC) correction, flat fielding and linearity correction have relatively small impacts on photometric precision.
In Figure \ref{fig:CV3pipeParamsWLP8} we show the standard deviation of the flux after averaging the A1 and B4 detectors and removing a linear trend.
We quote standard deviations for two example tests: SUB320 and FULL4.
The IPC corrections matter less than 0.01 ppm, because the deconvolution kernel conserves flux.
So long as the aperture is significantly wider than the 3$\times$3 pixel kernel, the flux in an aperture should be constant.
The flat fielding correction has less than a 2 ppm impact to the standard deviation because the image motion is at the sub-pixel level.

The linearity correction does consistently increase the signal to noise by 7 to 23 ppm but this is a natural consequence of the np photodiode in our detectors.
This is because the photodiode becomes decreasingly less sensitive to photons as it the well capacity is approached.
Note that at the extreme of saturation, the photodiode no longer senses new photons so you would measure a standard deviation of 0 ppm.
Therefore, the np photodiode naturally decreases the measured standard deviation of flux that will appear larger with a non-linearity correction.

>>>>

\usepackage{graphicx}
\usepackage{float}
\usepackage[caption=false]{subfig}
\usepackage{enumitem}
\listfiles

@@

\title{JWST Noise Floor I: Systematic Error Sources with JWST NIRCam Time Series}

@@

\author{Karl Misselt?}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

\author{Jarron Leisenring?}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

\author{Thomas Beatty?}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

\author{Thomas P Greene?}
\affiliation{NASA Ames Research Center \\
Space Science and Astrobiology Division \\
Moffett Field, CA 94035, USA}

\author{Peiman Maghami?}

\author{Michael McElwain}

@@

JWST transmission and emission spectra of transiting exoplanets will provide invaluable glimpses at exoplanet atmospheres.
These spectra will reveal the composition and temperature structure at a level never achieved before.
This promising science from JWST, however, will require exquisite precision and understanding of systematic errors that can impact the time series of planets crossing in front of and behind their host stars.
This is especially true if JWST is used to search for biosignatures in temperature atmospheres on Earth-sized planets that may contain liquid water.
Here, we provide estimates of the noise source affecting JWST NIRCam time series.
Correlated electronic noise (1/f noise) in the detectors can limit the sensitivity of grism time series for a given frame (300 ppm to 1000 ppm depending on the extraction method), but will average down like $\sqrt{N}$ for $N$ frames.
Care should be taken to include as many frames as possible per visit to reduce this 1/f noise source: thus, we recommend the smallest detector subarray sizes one can tolerate, 4 output channels and readout modes that minimize skipped frames (RAPID or BRIGHT2).
We also describe a covariance weighting scheme that can significantly lower the contributions from 1/f noise as compared to sum extraction.
Pointing jitter and high gain antenna moves on top of the detectors' subpixel crosshatch patterns will produce relatively small variations $\lesssim 10$ ppm, before they are corrected.
In contrast to the HST WFC3 detectors, persistence due to charge trapping will have a negligible effect on time series.
\end{abstract}

@@

Section \ref{sec:knownEffects} lists the known systematic effects that can impeded high precision time series and increase the noise above the photon and read noise.

\section{List of Known Detector Effects}\label{sec:knownEffects}
An ideal HgCdTe detector simply counts the photons incident on its surface (as described in section \ref{sec:detectorPrimer}).
However, there are many non-ideal effects that can affect the stability of a light curve of a transiting exoplanet.
Here, we review many of the known noise sources that could impact the stability of a time series beyond photon counting statistics. These known detector effects that can impact stability are listed briefly and then in more detail as related to the JWST NIRCam detectors below that.

@@

\section{Pre-amp Reset Offsets from the Lockheed CV Test}\label{sec:preAmp}

@@

\clearpage
\section{1/f Noise}
The readout circuitry for NIRCam and other JWST NIR instruments introduces correlated noise from pixel-to-pixel.
This is visible when examining the time series of pixels as they are read out within a frame in the order they are addressed.\footnote{See a diagram of the readout directions at \url{https://jwst-docs.stsci.edu/near-infrared-camera/nircam-instrumentation/nircam-detector-overview/nircam-detector-readout}}
The power spectrum of this pixel-by-pixel time series reveals high power at low frequencies that drops approximately like a 1/f power law in the power spectrum of the time series.
Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from amplifier over 108 dark frames.
To create the periodogram, the reference pixels are used to remove amplifier offsets between frames.
Next, the average of all frames is subtracted to remove the bias and all pixels that deviate by more than 80 DN from the average are masked to eliminate bad pixels.
The periodogram shows many spikes at high frequency including one at the line reset time of 524 clock cycles, which is the time to read out all the pixels in a row for the amplifier and line overheads before moving to the next row.

@@

\subsection{Long Darks}\label{sec:longDarks}

@@

\subsection{Mean Row by Amplifier}\label{sec:indAmpAvg}
A slight modification to the above strategy is to average each amplifier individually.
This takes care of any differences between amplifiers.
This individual amplifier dramatically decreases the errors.
The standard deviations of the background-subtracted photometry range from 2,540 to 3,300 DN or 65 to 85 ppm.
Therefore, this simple approach can dramatically decrease the 1/f noise to below the photon limit.
This is possible for Weak Lens photometry but not grism spectroscopy when dispersed parallel to detector rows (the fast-read direction).

\subsection{Smoothed Kernel Subtraction}\label{sec:smoothKernelSub}

@@

\subsection{Reference Channel Subtraction}
We note that the 4 channels can sometimes exhibit the same 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by un-illuminated channels.
We attempt to subtract an amplifier 0's time series from all amplifiers.
Of course, this means that this amplifier is perfectly subtracted and no noise or signal remains in this 1/4 of the image.
The subtraction step should increase the read noise on an individual pixel by $\sim \sqrt{2}$ because the errors from the subtracted pixel should add in quadrature to the original pixels.
This increase in read noise on a per-pixel level might be acceptable if it decreases the correlated errors along the rows.
On the other hand, if the each amplifier exhibits its own individual correlated noise behavior, the reference amplifier will fail to subtract out all correlated noise and may introduce more noise.

@@

\subsection{PCA Correction}
Another approach to treating the 1/f noise is dimensionality reduction with Principal Component Analysis.
Here, we assume that the counts for each pixel along a column is a random variable that can be correlated with pixels in other columns.
Each row represents a different noise iteration.
First, we calculate the mean value of each pixel in the 108 group stack and subtract all groups by this mean image.
This removes all bias levels and focuses on the time variability of the pixels.
Here, we assume the dark current is negligible.
Next, we mask all bad pixels by setting all pixels with $| f | > 200$ DN to 0 DN to remove bad pixels that can drive the principal components.
The first 10 principal components are plotted in Figure \ref{fig:pcaEigenvectors} for two example groups (54 and 55).

@@

\subsection{Grism Aperture}
The NIRCam grism time series are particularly susceptible to 1/f noise because the dispersion direction is parallel to the detector's fast-read direction.
This is visible in Figure \ref{fig:longDarkGrism} where the grism apertures (in red) are parallel to the 1/f noise correlations.
The background subtraction along the spatial direction (vertically) will efficiently remove pre-amplifier offsets from frame to frame and amplifier to amplifier.
However, there are no side reference pixels or horizontally-offset background regions available on the middle two amplifiers.
Therefore, the 1/f noise will adversely impact broadband behaviors of the lightcurves, especially on the middle two amplifiers.

@@

\subsection{Optimally Co-Variance Weighted Flux}\label{sec:optimalCovWeights}

@@

\subsection{Empirical Covariance Matrix}\label{sec:empCovarianceMatrix}
The ideal weighting of the spectrum from Equation \ref{eq:covarianceweights} depends on the covariance matrix $C_{ij}$.
We use CDS (correlated double sampling) read pairs of OTIS long dark data (108 frames) with reference pixel corrections to estimate $C_{ij}$.
We consider a wavelength bin that is 100 pixels in the dispersion direction (0.1$\mu$m) and 14 spatial spatial pixels.
We also subtract the CDS frames by the median of each row-by-row and the median of each column column-by-column to reduce the amplifier offsets and 1/f noise as done in Figure \ref{fig:longDarkPhot}.

@@

%% See the notebooks wlp8_psf_image.ipynb and noise_sources_wlp8.ipynb for calculations
\subsection{The impact of correlated read noise on time series}
We consider here some example science impacts of correlated read noise in these photometric apertures.
We will evaluate the performance of a WEAK LENS +8 mode photometric time series, as will be common with NIRCam grism time series observations.
For a pessimistic scenario, we assume a 15,000 DN read noise contributes to every pair of reads for the 70 pixel radius aperture (and 75 to 100 pixel background subtraction annulus).
If the read noise is tolerable under this scenario, then it should have a minimal impact on photometric time series.
If it is a problem, we will discuss methods of mitigation such as the row-by-row subtraction above.

@@

\subsection{Impact to Grism Time series}
We consider a 0.17$\mu$m-wide wavelength bin and 20 pixel aperture diameter as a test case for how badly it will impact spectroscopic features that are 0.17$\mu$m wide.
In this case, we assume row-by-row subtraction is performed and that the CDS noise from the OTIS ground-based test is representative of flight.
Then, the equivalent grism aperture noise to equation \ref{eq:bestRNCorrection} is
\begin{equation}
RN_{grism,0.17\mu\mathrm{m}} = \frac{5,130 DN}{ \sqrt{N_{frames}}}.
\end{equation}
For the grism aperture

\clearpage
\section{Fringing}

\clearpage
\section{Subpixel Crosshatching}

\subsection{Crosshatch Pattern Modeling}
We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency than in spatial coordinates as seen in Figure \ref{fig:crossHatchA5}.
We divide the 2D Fourier power spectral density by the number of pixels in an input image.
This was experimentally determined to give a power spectral density that does not change with the dimensions of the input image.
\textcolor{red}{Can we justify this more? I thought it would be pixels$^2$}

\clearpage
\subsection{Position of SubGrism Array}

\subsection{Subpixel Crosshatching Calculation}\label{sec:CrosshatchSim}

\subsection{Time Series Simulation}
The JWST fine steering mirror (FSM) is designed to correct any telescope pointing errors that are not full corrected by the reaction wheels.
The JWST attitude control system team provided a simulation of the expected pointing performance shown in Figure \ref{fig:tserPointingFull}.
